Improved Global Routing By Using A Star Algorithm

### 2020-05-31 paper.tex
Error In Build

\begin{abstract}
    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken. From the comparisons of the paper we can find that using any algorithm is a trade off as when time taken is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding path is a good approach to be used in global routing as it decreases the routing time and achieve the minimum wirelength.
\end{abstract}

@@

Routing is critical step in physical design process. Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered as a very interesting challenging field. It is exactly done in two steps, global routing and detailed routing. At first global routing is run which is the responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system. That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcame to make a correct routing process. First of all the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so wetotal wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip. There is another problem as circuits are made in nano-scale which means that its geometric will be complex. Another problem is that routing algorithm have to be applicable for more than one layer with different costs. The direction of wires also have to taken into consideration as the direction of wires in every layer can be either vertical or horizontal and no diagonal paths, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions that specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it have to go through via which have a high resistance. DFM (design for manufacturer) rules also has to be achieved. All of these constraints must be taken into consideration with the global routing to achieve hundred percent of the circuit connections, that means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with minimum time taken.

@@

Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some paperes tried to decrease number of vias, other papers tried to decrease the time taken and so on. In \cite{b2} they used two bounded length maze algorithms as finding path algorithms in order to make the router faster, the first one is optimal-BLMR which is used to get the minimum cost paths to be used as a routing paths, this can be done in three steps, first BLC (bounded length constraint) is defined as grater than Manhattan distance then to go from source to target the neighbour points are tested if it can be a part of path or not, each point that violates the BLC constraint is discarded, second

@@

\bibitem{b1} Muhammet Mustafa Ozdal and M. D. F. Wong, "Archer: a history-driven global routing algorithm," \textit{2007 IEEE/ACM International Conference on Computer-Aided Design}, San Jose, CA, 2007, pp. 488-495, doi: 10.1109/ICCAD.2007.4397312.

\bibitem{b2} Liu, Wen-Hao, et al. "NCTU-GR 2.0: Multithreaded collision-aware global routing with bounded-length maze routing." \textit{IEEE Transactions on computer-aided design of integrated circuits and systems} 32.5 (2013): 709-722.

>>>>

\begin{abstract}
    In this paper VLSI routing is improved by improving global routing, this can be done by using A-Star with a heuristic cost function that has parameters which affect the time taken by the router on changing instead of Dijkstra's algorithm in finding path, which will reduce the time taken in this process and achieve the minimum wirelength, many comparisons are taken in this paper with different algorithms to find the optimum algorithm to be used to achieve both minimum wirelength and minimum time taken. From the comparisons of the paper, we can find that using any algorithm is a trade-off as when the taken time is decreased, the wirelength is increased and vice versa, so there is no algorithm which is better from the other algorithms in general but using A-Star algorithm with the heuristic function in finding the path is a good approach to be used in global routing as it decreases the routing time and achieves the minimum wirelength.
\end{abstract}

@@

Routing is a critical step in the physical design process. Until now the optimum solution for VLSI routing has not been achieved yet, so it is considered a very interesting challenging field. It is exactly done in two steps, global routing, and detailed routing, in global routing, A-technique for 3D global routing is to compress a \textit{3D} grid into a \textit{2D} grid and handle \textit{2D} global routing. The obtained solution is then projected back to \textit{3D} by assignment of layers. as introduced in most of modern designs as in \cite{b1}, \cite{b2}, \cite{b3}, \cite{b4}, \cite{b5}, \cite{b6}, \cite{b7}, and \cite{b8}. At first global routing is run which is responsible for making an approximate routing for the whole circuit in order to be used as a guide for detailed routing, then the detailed routing is run to make the exact routing for the system. That means if global or detailed routing is improved the whole routing process is improved, but there are many problems that have to be overcome to make a correct routing process. First of all, the scale has to be taken into consideration, as millions of wires exist in a small chip area which means that many kilometers of wires are placed in a very small area, so total wirelength has to be minimized as much as possible, also it is known that as the wirelength increases the resistance increases as well which means more delay in the chip. There is another problem as circuits are made in nano-scale which means that its geometric will be complex. Another problem is that the routing algorithm has to be applicable for more than one layer with different costs. The direction of wires also has to be taken into consideration as the direction of wires in every layer can be either vertical or horizontal and no diagonal paths, then to go from source 'S' to target 'T' the path taken should be in (vertical | horizontal) directions that specified by the layer (at each layer wires are placed in one direction only), then there is another problem as when a wire goes from layer to another to continue on the perpendicular direction it has to go through via which has a high resistance. DFM (design for manufacturer) rules also have to be achieved. All of these constraints must be taken into consideration with the global routing to achieve a hundred percent of the circuit connections, which means global routing will take a lot of time to achieve all these constraints, and here is the challenge to achieve all the routing specifications with the minimum time taken.

@@

Several papers proposed various types of approaches to improve the routing process, each of them tried to improve the overall routing by improving one or more parameters, some papers tried to decrease the number of vias, other papers tried to decrease the time taken and so on.
\par
In \cite{b1} a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR. optimal-BLMR is used to get the minimum cost paths to be used as routing paths, this can be done in three steps. First BLC (bounded length constraint) is defined as a greater number than Manhattan distance then to go from source to target the neighbor points are tested if it can be a part of a path or not, each point that violates the BLC constraint is discarded. Second, if the route started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path. Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing. Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wirelength is enough to detour around congested regions. The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router between $2.71$ and $3.12$ in overflow free cases, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR). But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wirelength is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.
\par
In \cite{b4}

@@

    \bibitem{b1} Muhammet Mustafa Ozdal and M. D. F. Wong, \char`\"{}Archer: a history-driven global routi algorithm,\char`\"{} \textit{2007
    IEEE/ACM International Conference on Computer-Aided Design}, San Jose,
    CA, 2007, pp. 488-495, doi: 10.1109/ICCAD.2007.4397312.

    \bibitem{b2} Chang, Yen-Jung, Yu-Ting Lee, and Ting-Chi Wang. "NTHU-Route 2.0: a fast and stable global router." \textit{2008 IEEE/ACM International Conference on Computer-Aided Design. IEEE}, 2008.

    \bibitem{b3} H.-Y. Chen, C.-H. Hsu, and Y.-W. Chang, “High-performance global routing with fast overflow reduction,” \textit{in 2009 Asia and South Pacific Design Automation Conference}, pp. 582–587, IEEE, 2009.

    \bibitem{b4} Xu, Yue, Yanheng Zhang, and Chris Chu. "FastRoute 4.0: global router with efficient via minimization." \textit{2009 Asia and South Pacific Design Automation Conference. IEEE}, 2009.

    \bibitem{b5} Cho, Minsik, et al. "BoxRouter 2.0: Architecture and implementation of a hybrid and robust global router." \textit{2007 IEEE/ACM International Conference on Computer-Aided Design. IEEE}, 2007.

    \bibitem{b6} Ozdal, Muhammet Mustafa, and Martin DF Wong. "Archer: a history-driven global routing algorithm." \textit{2007 IEEE/ACM International Conference on Computer-Aided Design. IEEE}, 2007.

    \bibitem{b7} Gao, Jhih-Rong, Pei-Ci Wu, and Ting-Chi Wang. "A new global router for modern designs." \textit{2008 Asia and South Pacific Design Automation Conference.} IEEE, 2008.

    \bibitem{b8} Moffitt, Michael D. "MaizeRouter: Engineering an effective global router." \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems} 27.11 (2008): 2017-2026.

    \bibitem{b9} Roy, Jarrod A., and Igor L. Markov. "High-performance routing at the nanometer scale." \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems} 27.6 (2008): 1066-1077.
